\documentclass{letter}


\begin{document}
\begin{letter}

    \opening{Dear Hiring Manager,}

    I am newly minted mathematics Ph.D. graduate looking to become a software
    engineer. My Ph.D. thesis is on Computational Number Theory where I
    developed and implemented algorithms for computing certain invariants of
    modular abelian varieties.

    As a result of my graduate research work, I have developed strong technical
    skills. In particular, I made heavy use of Sagemath which is a Python
    mathematics library, similar to scipy, more suitable for research-level
    number theory computations. The results of my computations were then stored
    in PostgreSQL databases.

    The best part about Sagemath is that it is open source. My involvement in
    Sagemath began with my successful Google Summer of Code 2016 project in
    improving the modular abelian varieties functionality of Sagemath. This
    work would become the foundation of the computation-aspects of my Ph.D.
    thesis. I am still an active developer for Sagemath having authored 25
    tickets (19 accepted so far) and done code reviews for 10 tickets.

    Though my undergraduate and graduate degrees are in mathematics, I have
    taken numerous computer science classes as an undergraduate. In addition to
    the usual data structures and algorithms classes, I have taken formal
    languages and automata, two cryptography classes, and a graduate level
    logic class.

    I believe that the completion of my Ph.D. shows both my capacity to learn
    and the ability to undertake and complete long and difficult independent
    projects. In addition, I hope my Sagemath contributions shows both my
    passion and readiness for software engineering.

    If you have any questions at all, feel free to contact me either at
    \verb+626-310-2108+ or \verb+kevinywlui@gmail.com+.

    \closing{- Kevin Lui}

\end{letter}
\end{document}
