\documentclass{letter}


\begin{document}
\begin{letter}
    \opening{Dear Hiring Manager,}

    I am a newly minted Ph.D. graduate in computational number theory under
    William Stein. I am very interested in joining Galois -- particularly the
    cryptography team.
    
    I should begin by stating that I do not have a research-level understanding
    of cryptography but I do have a research-level understanding of some
    closely-related math topics. My thesis centered around creating and
    implemented algorithms for computing with modular abelian varieties which
    are higher-dimensional versions of elliptic curves. Consequently, I have a
    strong background in computing with elliptic curves.

    Most of my cryptography knowledge came from when I was an undergraduate at
    UC Santa Barbara. I took the usual introduction to cryptography class as
    well as a special topics class on random number generators. But perhaps the
    most educational experience was attending CRYPTO 2013. I found some talks
    and the rump session very interesting which solidified my enthusiasm for
    cryptography.  

    Like Galois, I value contributing to open-source software. I am a regular
    user and developer for the Sagemath project. Sagemath is an open-source
    Python package, similar to numpy, but more suitable for research-level
    number theory computations. My contributions began with a Google Summer of
    Code project with Sagemath where I improved the functionality of the
    modular abelian variety component. The work here eventually morphed into my
    Ph.D. thesis. Since then I have authored 25 tickets (19 accepted) and
    have reviewed 10 tickets so far. My work for Sagemath has been invaluable
    towards my software training.

    I understand that Galois uses Haskell which I find enticing. I have learned
    Haskell in the past as part of a computer theorem proving class but have
    not used it much since. If given the opportunity to join Haskell, I am more
    than willing to pick it up again.

    I understand that my background is not the perfect fit for this position.
    But I hope that my thesis work and my Sagemath contributions demonstrates
    that I can still make valuable contributions to the team.

    \closing{- Kevin Lui}

\end{letter}
\end{document}
